\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/ms.tex
plot confidence vs. performance in main text
ensure links for all variables

\begin{figure}
    \centering
    %\includegraphics{figures/estimated_difficulty.pdf}
    \caption{Caption}
    \label{fig:estimated_difficulty}
\end{figure}

@@

To ensure that the questions do not enter a training dataset we use the canary string of the Big Bench project.
This requires that \Gls{llm} developers filter their training dataset for this canary string.

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/confidence_vs_performance_overall.pdf}
    \caption{\textbf{Relationship between confidence of the model in the answer and correctness.}}
    \label{fig:confidence_vs_performance}
    \script{joint_analysis_confidence_performance.py}
\end{figure}

@@

To ensure that the questions do not enter a training dataset we use the canary string of the Big Bench project.
This requires that \Gls{llm} developers filter their training dataset for this canary string.\cite{openai2024gpt4, srivastava2022beyond}
